The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-08 paper/main.tex
paper: incorporate KM comments

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
both planet radii and stellar properties.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
searchable point on the sky might be two searchable stars.
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars.

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of searchable stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity fraction 
of stars that are searchable for a given observed transit depth is greater 
than that the multiplicity fraction in a volume limited sample.
This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
are searchable out to larger distances than single stars because they are more 
luminous.
A separate effect is that the apparent radii assigned to planets in binaries 
will typically be smaller than the true radii.
Correcting for ``radius dilution'' requires knowing both the amount flux 
contributed by each source in a photometric aperture, and which star the 
planet orbits.

@@

First, what are the possible apparent radii of detected planets?
If the true planet radius is $r=r\p$, then planets in singles will be 
detected with identical apparent radii: $r\a = r\p$.
Conversely, all detections in twin binaries will have apparent radii 
$r\a=r\p/\sqrt{2}$, because they are diluted.
For an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}(M_1, q)},
\label{eq:delta_obs_general} 
\end{equation}
where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
ratio.
We assume that the stellar radius and luminosity are uniquely related to the 
stellar mass.
The observers, with no a priori knowledge of the distance to a system, would 
measure a flux, assume a stellar mass $M\a=M_1$, and estimate a stellar 
radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
sys,a}(M\a) = L(M\a)$.

@@

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}$ is the volume-limited binary fraction, and $\mathcal{A}$ 
($\mathcal{B}$) is the dilution term for primaries (secondaries).
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).
The rate densities depend on both apparent radius and mass 
because even if the primaries and singles were to have fixed
mass, the mass of secondaries would vary, and so this dependence cannot be 
immediately omitted.

A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
\hyperref[sec:appendix]{Appendix}; here we highlight its qualitative 
features.
The terms inside the curly braces $\{ \ldots \}$ are the sum of 
the apparent rate densities from singles, primaries, and secondaries.
The contribution from singles is not affected by binarity.
In the contributions from primaries and secondaries,
planets with $(r\a, M\a)$ are associated with 
systems of different planetary and stellar properties, as determined
by the mass ratio $q$ of each binary.
This corresponds to true planet radii and stellar masses 
$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
secondaries.
These contributions are then integrated over the mass ratio distribution 
including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
further below. Finally, the latter term in the apparent rate density of 
secondaries comes from a correction for the overestimated transit probability.

@@

This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance.
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Eq.~\ref{eq:general_Gamma_a} over apparent stellar mass, we find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}\times 
\left(
\int {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int {\rm d}q\,q^{\beta+\gamma+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right].
\label{eq:powerlaw_vary_binary}
\end{align}

For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power-law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.

@@

\paragraph{Hot Jupiter occurrence rates}
Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
we can compare the apparent hot Jupiter 
occurrence rate with the true rate for singles.
In the most extreme case of $Z_2/Z_0=0$, we find that $\Lambda_{{\rm 
HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
\begin{equation}
\Lambda_{\rm HJ,a} = \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
\end{equation}
and similarly for $\Lambda_{\rm HJ,0}$.
%occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less: when 
$Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$

@@

Further, Fig.~\ref{fig:frac_model_3} shows that going from apparent 
radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
planets with binary companions increases by $\approx 6-12\%$, depending on the 
assumed value of $Z_2/Z_0$.
Let the fraction of total detected planets from primaries at a given 
apparent radius be $F_1(r\a)$, and from secondaries let it be $F_2(r\a)$.
In the planet-less secondaries case ($F_2(r\a)=0$), one can 
analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
that $F_1(2r_\oplus)/F_1(2r_\oplus/\sqrt{2}) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0
Intuitively speaking, this ``shift'' is a feature of any radius distribution 
that declines at large radii, and flattens below some cutoff $r_{\rm c}$.
This is because (for dilution about primaries)
at apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets will be 
``diluted'' into the given $r\a$, since there are more planets in 
the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
This prediction is compared against current measurements in 
Sec.~\ref{sec:discussion}.

@@

In the recent work by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
island in period-radius space, rather than as a continuous component of a 
power law distribution.
This means that the apparent HJ rates computed in 
Sec.~\ref{sec:model_3} are probably inaccurate.
If we instead consider a Gaussian radius shape function,
\begin{equation}
f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
\end{equation}
with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.
As always, $\Gamma_i(r) = Z_i f(r)$.
We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
Integrating to find hot Jupiter rates,
we find the opposite effect as in the power law model.
For $Z_2/Z_0>0$, 
the apparent HJ rate is {\it greater} than the true rate for singles.
The effect is maximal when there are as many hot Jupiters orbiting secondaries 
as singles, in which case
$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
%int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
\approx \Lambda_{\rm HJ,a}$ to within one percent.

@@

\paragraph{The rate of Earth analogs}
In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
planets orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts revealed that the one-year terrestrial planet occurrence rate 
is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
depending on assumptions that are made when calculating the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In Sec.~\ref{sec:model_3}, our power law model indicates that when singles and 
secondaries host the same number of planets, the apparent rate is 50\% higher 
than the true rate around single stars.
Though this bias seems large, it is currently smaller than the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity will likely merit closer attention.

@@

\paragraph{Hot Jupiter rate discrepancy}
While binarity may appreciably affect $\eta_\oplus$ measurements, our analysis
suggests that it is unlikely to influence the hot Jupiter rate discrepancy.
The context of this disagreement is that hot Jupiter occurrence rates measured 
by transit surveys ($\approx 0.5\%$) are marginally lower than those found by 
radial velocity surveys ($\approx 1\%$; see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
    [{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
0.7$, and noted that this would imply that the metallicity difference could 
account for a $\approx 20\%$ relative difference in the measured rates between 
the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
    \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
    This gives an $\approx 25\%$ relative difference, indicating metallicity 
    could 
    account for about half of the ``hot Jupiter rate discrepancy''.
}.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

@@

Of course, such calculations are only suggestive; a conclusive resolution 
of binarity's effects may require a detailed understanding of the 
{\it Kepler}\ field's multiplicity statistics, and the mission's completeness 
(both for candidate detection and follow-up).
For instance, if hot Jupiters are less likely to be confirmed in binary 
systems, this might bias the rates low.
Alternatively, {\it TESS}\ is expected to discover over $10^4$ 
giant planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
Though they will be difficult to distinguish from false positives, one 
possible use of this sample will to measure an occurrence rate of 
short-period giant planets with minimal error from counting statistics.
Our models suggest that binarity will only become an appreciable fraction of 
the error budget at the $\approx 10\%$ precision level.
This should be sufficient for a rate measurement precise enough to indicate a 
preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
hot Jupiters.

@@

In this appendix, we derive Eq.~\ref{eq:general_Gamma_a}.
First, recall our definition of apparent rate density 
(Eq.~\ref{eq:defn_apparent_rate_density}).
Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
determined from the assumed stellar mass--radius--luminosity relation. We 
neglect the dependence on planetary orbital period.
The planets with $(r\a, M\a)$ are associated with 
systems of many different planetary and stellar properties, so $n_{\rm 
det}(r\a, M\a)$ is given by the convolution of the true rate density, 
$\Gamma(r, M)$, and $\mathcal{N}(r\a, M\a; r, M)$, the number (per 
unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
the true system actually has $(r, M)$. Mathematically,
\begin{align}
n_{\rm det}(r_a, M_a) &=
\sum_i n_{\rm det}^i(r_a, M_a) \\
&=
\sum_i \int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
\cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
\label{eq:n_det}
\end{align}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
secondary).
The problem reduces to the evaluation of
\begin{equation}
\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in 
binaries.

@@

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r_a,M_a)$ given the 
true parameters $(r,M)$ is
\begin{equation}
\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a, q; r, M),
\label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.

>>>>

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
both planet radii and stellar properties.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
searchable point on the sky might be two searchable stars.
Finally, there are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in 
binaries may have different masses and radii than assumed in the single-star 
case.

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of searchable stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity fraction 
of stars that are searchable for a given observed transit depth is greater 
than the multiplicity fraction in a volume limited sample.
This is the familiar Malmquist bias: at a fixed $\delta_{\rm obs}$, binaries 
are searchable out to larger distances than single stars because they are more 
luminous.
A separate effect is that the apparent radii assigned to planets in binaries 
will typically be smaller than the true radii.
Correcting for ``radius dilution'' requires knowing both the amount flux 
contributed by each source in a photometric aperture, and which star the 
planet orbits.

@@

First, what are the possible apparent radii of detected planets?
If the true planet radius is $r=r\p$, then planets in singles will be 
detected with identical apparent radii: $r\a = r\p$.
Conversely, all detections in twin binaries will have apparent radii 
$r\a=r\p/\sqrt{2}$, because they are diluted.
For an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}(M_1, q)},
\label{eq:delta_obs_general} 
\end{equation}
where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
ratio.
We assume that the stellar radius and luminosity are uniquely related to the 
stellar mass.
The observers, with no a priori knowledge of the distance to a system, would 
measure a flux, and estimate a stellar mass $M\a=M_1$, a stellar 
radius $R\a = R(M\a)$, and an under-estimated system luminosity of $L_{\rm 
sys,a}(M\a) = L(M\a)$.

@@

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int_0^1 \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int_0^1 {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}$ is the volume-limited binary fraction, 
and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
primaries [secondaries], whose functional dependences are omitted for 
notational simplicity.
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).
The rate densities depend on both apparent radius and mass 
because even if the primaries and singles were to have fixed
mass, the mass of secondaries would vary, and so this dependence cannot be 
immediately omitted.

A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
\hyperref[sec:appendix]{Appendix}; its qualitative features are as follows.
The terms inside the curly braces $\{ \ldots \}$ are the sum of 
the apparent rate densities from singles, primaries, and secondaries.
The contribution from singles is not affected by binarity.
In the contributions from primaries and secondaries,
planets with $(r\a, M\a)$ are associated with 
systems of different planetary and stellar properties, as determined
by the mass ratio $q$ of each binary.
This corresponds to true planet radii and stellar masses 
$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
secondaries.
These contributions are then integrated over the mass ratio distribution 
including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
further below. Finally, the latter term in the apparent rate density of 
secondaries comes from a correction for the overestimated transit probability.

@@

This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance;
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Eq.~\ref{eq:general_Gamma_a} over apparent stellar mass, we find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{{\rm BF}}{1-{\rm BF}}\times 
\left(
\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right],
\label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over $M\a$.
For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power-law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.

@@

\paragraph{Hot Jupiter occurrence rates}
Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
we can compare the apparent hot Jupiter 
occurrence rate with the true rate for singles.
In the most extreme case of $Z_2/Z_0=0$, we find that $\Lambda_{{\rm 
HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
\begin{equation}
\Lambda_{\rm HJ,a} = \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
\end{equation}
and similarly for $\Lambda_{\rm HJ,0}$.
%occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
If $Z_2/Z_0>0$, binarity affects the apparent hot Jupiter rate less: when 
$Z_2/Z_0=0.5$, we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$.

@@

Further, Fig.~\ref{fig:frac_model_3} shows that going from apparent 
radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
planets with binary companions increases by $\approx 6-12\%$, depending on the 
assumed value of $Z_2/Z_0$.
Let the fraction of total detected planets from primaries at a given 
apparent radius be $F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm 
det}^{\rm tot}$.
Let the analogous quantity for secondaries be $F_2(r\a)$.
In the planet-less secondaries case ($F_2(r\a)=0$), one can 
analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0
Intuitively speaking, this ``shift'' is a feature of any radius distribution 
that declines at large radii, and flattens below some cutoff $r_{\rm c}$.
This is because (for dilution about primaries)
at apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets will be 
``diluted'' into the given $r\a$, since there are more planets in 
the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
This prediction is compared against current measurements in 
Sec.~\ref{sec:discussion}.

@@

In the recent work by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
island in period-radius space, rather than as a continuous component of a 
power law distribution.
This means that the apparent HJ rates computed in 
Sec.~\ref{sec:model_3} are probably inaccurate.
Instead, let us consider a Gaussian radius shape function,
\begin{equation}
f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
\end{equation}
with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.
As always, $\Gamma_i(r) = Z_i f(r)$.
We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
Integrating for $r\a > 8r_\oplus$ to find hot Jupiter rates,
we find the opposite effect as in the power law model.
For $Z_2/Z_0>0$, 
the apparent HJ rate is {\it greater} than the true rate for singles.
The effect is maximal when there are as many hot Jupiters orbiting secondaries 
as singles, in which case
$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
%int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
\approx \Lambda_{\rm HJ,a}$ to within one percent.
Qualitatively, the apparent HJ rate can be greater than the true rate for 
singles because binary systems can have an extra star that yields 
hot Jupiter detections.

@@

\paragraph{The rate of Earth analogs}
In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
planets orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts revealed that the one-year terrestrial planet occurrence rate 
is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
depending on assumptions that are made when calculating the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In Sec.~\ref{sec:model_3}, our power law model indicates that when primaries, 
singles, and secondaries host the same number of planets, the apparent rate is 
50\% higher than the true rate around single stars.
Though this bias seems large, it is currently smaller than the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity will likely merit closer attention.

@@

\paragraph{Hot Jupiter rate discrepancy}
While binarity may appreciably affect $\eta_\oplus$ measurements, our analysis
suggests that it is unlikely to influence the hot Jupiter rate discrepancy.
The context of this disagreement is that hot Jupiter occurrence rates measured 
by transit surveys ($\approx 0.5\%$) are marginally lower than those found by 
radial velocity surveys ($\approx 1\%$; see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
    [{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
0.7$, and noted that this would imply that the metallicity difference could 
account for a $\approx 20\%$ relative difference in the measured rates between 
the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
    \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
    This gives a $\approx 25\%$ relative difference, indicating metallicity 
    could 
    account for about half of the ``hot Jupiter rate discrepancy''.
}.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

@@

Of course, such calculations are only suggestive; a conclusive resolution 
of binarity's effects may require a detailed understanding of the 
{\it Kepler}\ field's multiplicity statistics, and the mission's completeness 
(both for candidate detection and follow-up).
For instance, if hot Jupiters are less likely to be confirmed in binary 
systems, this might bias the rates low.
Alternatively, {\it TESS}\ is expected to discover over $10^4$ 
giant planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
Though they will be difficult to distinguish from false positives, one 
possible use of this sample will be to measure an occurrence rate of 
short-period giant planets with minimal error from counting statistics.
Our models suggest that binarity will only become an appreciable fraction of 
the error budget at the $\approx 10\%$ precision level.
This should be sufficient for a rate measurement precise enough to indicate a 
preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
hot Jupiters.

@@

In this appendix, we derive Eq.~\ref{eq:general_Gamma_a}.
First, recall our definition of apparent rate density 
(Eq.~\ref{eq:defn_apparent_rate_density}).
Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
determined from the assumed stellar mass--radius--luminosity relation. We 
neglect the dependence on planetary orbital period.
The planets with $(r\a, M\a)$ are associated with 
systems of many different planetary and stellar properties, so $n_{\rm 
det}(r\a, M\a)$ is given by the convolution of the true rate density, 
$\Gamma(r, M)$, and $\mathcal{N}(r\a, M\a; r, M)$, the number (per 
unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
the true system actually has $(r, M)$. Mathematically,
\begin{align}
n_{\rm det}(r_a, M\a) &=
\sum_i n_{\rm det}^i(r_a, M\a) \\
&=
\sum_i \int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^i(r_a,M\a; r,M)
\cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
\label{eq:n_det}
\end{align}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
secondary).
The problem reduces to the evaluation of
\begin{equation}
\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in 
binaries.

@@

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r_a,M\a)$ given the 
true parameters $(r,M)$ is
\begin{equation}
\mathcal{N}_{\rm s}^1(r_a, M\a; r, M)
=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M\a, q; r, M),
\label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.
